Novelty Detection Using Graphical Models for Semantic Room Classification

### 2011-05-17 semantic-nd/article.tex
Changed the initial part of novelty detection to show that the threshold is optimal.

% Explain threshold approach to novelty detection
Due to the desire of robustness and generalization, a novelty detection system would
always possess some threshold that describes on how strict the system should be to
new data.
This threshold describes a trade between error and rejection.
And is often seen as a distance measure to the known class.

When dealing with a statistic point of view, noisy data or unstable features, a decision on a
given input has an associated error rate. A novelty detection system is interested in defining an
order on all the possible inputs equivalent to the order imposed by the error rate: $P(novel|x)$.

Using bayes rule on the reversed order $P(\overline{novel}|x)$ and assuming a constant $P(\overline{novel})$
a ratio between a conditional and unconditional probabilities of the input $x$ is obtained.
Such a ratio is a suitable function for implementing an optimal novelty detector system with
thresholding.

>>>>

% Explain threshold approach to novelty detection
Due to the desire of robustness, a novelty detection system would
always possess some threshold that describes on how strict the system should be to
new samples. This threshold describes a trade between error and rejection: as the
more the system tries to reduce rejection the more prone to produce
errors it becomes.
This threshold if often seen as a max allowed distance between a sample and the known
class.

When dealing with a statistic point of view, noisy data or unstable features, a decision to
classify a sample as novel as an associated error probability of $P(\overline{novel}|x)$.
And the error rate of a system that classifies the set of inputs $N$ as novel is given by
the equation:

\begin{equation}
P(e) = \frac{\sum_{n \in N}{P(\overline{novel}|n)P(n)}}{\sum_{n \in N}{P(n)}}
\end{equation}

Therefore any novelty system that decides to acknowledge a sample
$a$ as novel should also detect novelty on any sample $b$ satisfying
$P(\overline{novel}|b) < P(\overline{novel}|a)$.
As that would always reduce the error probability.
This way a novelty detection system is interested in defining an
order on all the possible inputs equivalent to the order defined by
the error rate: $P(\overline{novel}|x)$.

Using Bayes rule and assuming a constant $P(\overline{novel})$
a ratio between a conditional and unconditional probabilities of the input $x$ is obtained.
Such a ratio is a suitable function for implementing a novelty detector system with optimal
thresholding.
